---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# missInfo

[![R-CMD-check](https://github.com/rpkgs/missInfo/workflows/R-CMD-check/badge.svg)](https://github.com/rpkgs/missInfo/actions)
[![codecov](https://codecov.io/gh/kongdd/missInfo/branch/master/graph/badge.svg)](https://codecov.io/gh/kongdd/missInfo)
[![License](http://img.shields.io/badge/license-GPL%20%28%3E=%203%29-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN](http://www.r-pkg.org/badges/version/missInfo)](https://cran.r-project.org/package=missInfo)

`missInfo` package is used to detect daily meteorological station data missing information and interpolate missing values.

------

 **Tasklist**:

- [ ] Add QC_flag for filled value

## Installation

You can install the released version of missInfo from [github](https://github.com/kongdd/missInfo) with:

``` r
devtools::install_github("kongdd/missInfo")
```

## Example

This is a basic example which shows you how to solve a common problem:

* **prcp** data.frame, with dimension of [n_date, 1+n_station], and the first column is date.
* **st840** data.frame, with columns at least of 'site', 'lat', 'lon' (degree).

```{r example}
library(missInfo)
## basic example code
data("prcp")
data("st840")
r <- interp_main(prcp, st840, smax = 200, verbose = FALSE)
```


## 气象要素特征值说明 (Illustration of meteorological flags)：

* 台站海拔高度  +100000 当台站海拔高度为估测值时，在估测数据基础上加100000

* 各要素项  32766 数据缺测或无观测任务

* 气压日极值 +20000  气压极值取自定时值，在原值上加20000

* 日最小相对湿度 +300  最小相对湿度取自定时值，在原值上加300

* 风速  +1000 当风速超过仪器测量上限时，在上限数据基础上加1000

* 风向  1-17  用数字表示风向方位，17表示静风
  +100  当表示风向为八风向时，在原值上加100
  90X 风向出现X个时，风向数据用个数X表示
  95X 风向至少出现X个时，风向数据用个数X表示

* 降水量   

  | flag | Description           |
  | ---- | --------------------  |
  |32700 | 表示降水"微量" (0.1mm) |
  |32XXX | XXX为*<u>纯雾露霜</u>* |
  |31XXX | XXX为<u>*雨和雪的总量*</u> |
  |30XXX | XXX为<u>*雪量(仅包括雨夹雪，雪暴）*</u> |

* 蒸发量   
  32700 表示蒸发器结冰
  +1000 蒸发器中注入的水全部蒸发，在注入的水量数据基础上加1000

* 0cm地温 
  +10000  实际温度（零上）超仪器上限刻度，在上限数据基础上加10000
  -10000  实际温度（零下）超仪器下限刻度，在下限数据基础上减10000

* *Quality Control (**QC**) flags*

  | flag | Description          |
  | ---- | -------------------- |
  | 0    | 数据正确             |
  | 1    | 数据可疑             |
  | 2    | 数据错误             |
  | 8    | 数据缺测或无观测任务 |
  | 9    | 数据未进行质量控制   |

# **References**


> \[1\] Dongdong Kong, R package: missing information detect and interpolate, `missInfo` version 0.1.1, <https://github.com/kongdd/missInfo>

# Acknowledgements

Keep in mind that this repository is released under a GPL-3 license, which permits commercial use but requires that the source code (of derivatives) is always open even if hosted as a web service.
